
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\usepackage{url}
 
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{N-Version Programming}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}


\author{Maximilian Stach}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Fakultät Informatik, TU Dortmund
%W\url{http://.ai.cs.tu-dortmund.de}
}



\maketitle


\begin{abstract}
In dieser Arbeit werden die Konzepte und Eigenschaften des N-Version Programming kurz vorgestellt. Desweiteren werden mögliche Anwendungsbereiche für N-Version Programming in sicherheitskritischen Softwarebereichen aufgezeigt und auf mögliche Kosten und Nutzen im Vergleich zu weiteren Programmierparadigmen eingegangen.
\keywords{N-Version Programming, Sicherheit von Softwarearchitekturen, Zero-Day Exploits,...}
\end{abstract}
\tableofcontents

\cleardoublepage

\section{Einleitung} \label{einleitung}
\input{kapitel/einleitung.tex}


\section{Stand der Forschung} \label{stand}
\input{kapitel/stand.tex}


\section{Definition} \label{definition}
\input{kapitel/nversion.tex}

\section{N-Version in durchgeführten Projekten} \label{beispiele}
\input{kapitel/beispiele.tex}

\section{Vergleich mit anderen Ansätzen} \label{bewertung}
\input{kapitel/bewertung.tex}

\section{Zusammenfassung und Ausblick} \label{zusammenfassung-ausblick}
\input{kapitel/zusammenfassung.tex}




\begin{thebibliography}{4}

\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
Subsequences. J. Mol. Biol. 147, 195--197 (1981)

\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
Composing a Complex Biological Workflow through Web Services. In: Nagel,
W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
pp. 1148--1158. Springer, Heidelberg (2006)

\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
Infrastructure. Morgan Kaufmann, San Francisco (1999)

\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
Information Services for Distributed Resource Sharing. In: 10th IEEE
International Symposium on High Performance Distributed Computing, pp.
181--184. IEEE Press, New York (2001)

\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
Grid: an Open Grid Services Architecture for Distributed Systems
Integration. Technical report, Global Grid Forum (2002)

\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}


\section*{Anhang}
\input{kapitel/anhang.tex}

\end{document}
